---
output:
  md_document:
    variant: markdown_github
---

```{r setup, echo = FALSE}
library("knitr")

opts_chunk$set(fig.align  = "center",
               fig.path   = "README/",
               cache.path = "README/cache/",
               comment    = "#>",
               warning    = FALSE,
               message    = FALSE)
```

<!-- README.md is generated from README.rmd. Please edit that file -->

# clouds

clouds is a package that implements non-parametric clustering algorithims
for groups of numeric data. A cloud is a numerical vector with a weight vector 
associated from which an empircal cumulative distribution function (ECDF) can be
computed.

clouds defines a pseudo-distance function to compare ECDFs. So given a set of 
clouds -- e.g. an experiment with a response variable and treatment groups, 
where each group will define a cloud -- a distance matrix for the clouds can be
computed. Based on this matrix we can apply different well-known clustering 
methods to group the clouds.

Currently there are two methods implemented `k_clouds` which uses k-means for 
the clustering and `j_clouds` which uses Ward's hierarchichal algorithm as 
implemented in `stats::hclust()` with `method = "ward.D"`.

### Installation

Install from GitHub with `devtools`:

```
devtools::install_github("nebulae-co/clouds")
```

### Usage

Lets make some data from five different normal distributions:

```{r data}
library("dplyr")

n_distributions <- 5L
n_groups <- 4L
group_size <- 12
N <- group_size * n_groups
distributions <- letters[1:n_distributions]
groups <- LETTERS[1:(n_distributions * n_groups)]

mean <- 1:5
sd <- c(2, 1, 0.5, 1, 2)

sample <- data_frame(
  y = c(mapply(rnorm, mean = mean, sd = sd, MoreArgs = list(n = N))),
  distribution = rep(distributions, each = N),
  group = rep(groups, each = group_size))

sample
```

Now lets load `clouds` and get the `k_clouds` clusters:

```{r k_clouds}
library("clouds")

sample %>%
  k_clouds(var = "y", group = "group", k = 5, threshold = 0.01)
```

Compare with the `j_clouds` clusters:
```{r j_clouds}
sample %>%
  j_clouds(var = "y", group = "group", k = 5)
```

### About

This is mostly result of [Julian](https://github.com/CruzJulian)'s research for
his [Master Thesis](https://github.com/CruzJulian/Tesis).

[Daniel](https://github.com/demorenoc) has done the packaging.

Still a work in progress.
